Do motif roles provide unique information about species risk of extinction?

### 2021-06-28 manuscript/motifs_vs_degree.tex

    \begin{figure}[h!]
        \includegraphics[width=.95\textwidth]{figures/persistence_positions_bymotif.eps}
        \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Relationships are shown for the range 0-0.8 for all positions, but some positions (especially in the omnivory motif) are less common. Line colour indicates the probability of extinction for basal resources. Line style indicates the number of prey within the motif for each position. Symbol shape indicates the number of predators within the motif for each position; note that only bottom-up extinctions were included in our simulations.}
        \label{figs:persistence_position_motifs}
        \end{figure}

>>>>

    \begin{figure}[h!]
        \includegraphics[width=.95\textwidth]{figures/persistence_positions_Omnivory.eps}
        \caption{A species' probability of persistence varied with the frequency of different motif positions in its role. Here we show the relationships between persistence and the proportions of the three positions in the omnivory motif at three levels of probability of extinction for basal resources (p=0.1, 0.26, and 0.42), indicated by line colour. Line style indicates the motif  position. }
        \label{figs:persistence_position_motifs}
        \end{figure}
